Supplementary Figure 1a

### 2017-12-04 inst/stable_line_pol2_chip/stable_line_pol2_chip.Rmd
fixing headers in Rmds
re-ran all rmds and added sessionInfo to all
lots of work on figures to improve readability

pdf <- p +
    geom_linerange(
    data = stats,
    aes(x = condition, ymin = CI95l, ymax = CI95h),
    colour = "gray20",
    size = 0.1,
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(x = condition, y = mean),
    colour = "gray20",
    shape = 95,
    show.legend = FALSE
  ) +
  geom_segment(
    data = filter(stats, condition == "PC3 miR34a\nasRNA"),
    aes(x = 1, y = CI95h + 0.25, xend = 2, yend = CI95h + 0.25),
    colour = "grey43",
    size = 0.1
  ) +
  geom_label(
    data = stats,
    aes(x = 1.5, y = CI95h + 0.45, label = pFormat),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 1.5,
    family = "Arial Unicode MS"
  )

>>>>

pdf <- p +
    geom_linerange(
    data = stats,
    aes(x = condition, ymin = CI95l, ymax = CI95h),
    colour = "gray20",
    size = 0.3,
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(x = condition, y = mean),
    colour = "gray20",
    shape = 95,
    size = 4,
    show.legend = FALSE
  ) +
  geom_segment(
    data = filter(stats, condition == "PC3 miR34a\nasRNA"),
    aes(x = 1, y = CI95h + 0.25, xend = 2, yend = CI95h + 0.25),
    colour = "grey43",
    size = 0.3
  ) +
  geom_label(
    data = stats,
    aes(x = 1.5, y = CI95h + 0.45, label = pFormat),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 2,
    family = "Arial Unicode MS"
  )

### 2017-12-04 inst/tcga_correlation/tcga_correlation.Rmd
lots of work on figures to improve readability

#save to pdf
# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure1c"][[1]])
# pdf(path, width = 28)
# data %>%
#   arrange(cancer_PAM50, TP53, RP3) %>%
#   plotTCGAcorrelation(type = "diploid only")
# invisible(dev.off())
```

>>>>

##save to pdf
# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure1c"][[1]])
# pdf(path, width = 7.7, height = 4)
# plotTCGAcorrelation(data, type = "diploid only")
# invisible(dev.off())
```

### 2017-12-04 inst/tcga_correlation_table/tcga_correlation_table.Rmd
lots of work on figures to improve readability

Note: in cases where less than 3 samples are in any group, r-estimates and p-values are not reported.
```{r, warning = FALSE}
url <- fileMap(type = "rds")["figure1c"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

#diploid only correlation analysis
#calculate correlation for all samples per cancer type
all <- data %>% 
  filter(RP3_cna < 0.1) %>%
  group_by(cancer_PAM50) %>%
  summarize(
    n = n(),
    all_pvalue = signif(cor.test(RP3, miR34a, method = "spearman")$p.value, 3),
    all_R_estimate = signif(cor.test(RP3, miR34a, method = "spearman")$estimate, 3)
  )

#calculate correlation for p53 wt and mut samples per cancer type
p53 <- data %>%
  group_by(cancer_PAM50, TP53) %>%
  filter(n() > 3) %>%
  summarize(
    n = n(),
    pvalue = signif(cor.test(RP3, miR34a, method = "spearman")$p.value, 3),
    R_estimate = signif(cor.test(RP3, miR34a, method = "spearman")$estimate, 3)
  ) %>%
  ungroup() %>%
  gather(metric, value, -(cancer_PAM50:TP53)) %>%
  unite(temp, TP53, metric) %>%
  spread(temp, value)

full_join(all, p53, by = "cancer_PAM50")
```

>>>>

Note: in cases where less than 3 samples are in any group, r-estimates and p-values are not reported.

```{r, warning = FALSE}
url <- fileMap(type = "rds")["figure1c"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

#diploid only correlation analysis
#calculate correlation for all samples per cancer type
all <- data %>% 
  filter(RP3_cna < 0.1) %>%
  group_by(cancer_PAM50) %>%
  summarize(
    n = n(),
    `all pvalue` = cor.test(RP3, miR34a, method = "spearman")$p.value,
    `all rho` = cor.test(RP3, miR34a, method = "spearman")$estimate
  ) %>%
  mutate(
    `all pvalue` = format(`all pvalue`, scientific = TRUE, digits = 3),
    `all rho` = format(`all rho`, scientific = TRUE, digits = 3)
  )

#calculate correlation for p53 wt and mut samples per cancer type
p53 <- data %>%
  group_by(cancer_PAM50, TP53) %>%
  filter(n() > 3) %>%
  summarize(
    n = n(),
    pvalue = cor.test(RP3, miR34a, method = "spearman")$p.value,
    rho = cor.test(RP3, miR34a, method = "spearman")$estimate
  ) %>%
  ungroup() %>%
  mutate(
    pvalue = format(pvalue, scientific = TRUE, digits = 3),
    rho = format(rho, scientific = TRUE, digits = 3)
  ) %>%
  gather(metric, value, -(cancer_PAM50:TP53)) %>%
  unite(temp, TP53, metric, sep = " ") %>%
  spread(temp, value)

table <- full_join(all, p53, by = "cancer_PAM50") %>%
  rename(cancer = cancer_PAM50, `all n` = n) %>%
  select(
    cancer, `all n`, `all rho`, `all pvalue`, `TP53wt n`, 
    `TP53wt rho`, `TP53wt pvalue`, `TP53mut n`, `TP53mut rho`, `TP53mut pvalue`
  )

table

path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1a"][[1]])
pdf(file = path, width = 14)
gridExtra::grid.table(table, rows = NULL)
invisible(dev.off())
```
